Beyoncé

### 2024-04-14 paper/paper.qmd
Fix some typos in paper

The dataset used in this paper was created using data gathered from Spotify [@spotify] and Billboard [@billboard]. The data was collected for the purpose of this paper to investigate the number of Spotify streams based on weeks spent on the *Billboard Hot 100* for Beyoncé songs. Song titles, album titles, and the number of Spotify streams were collected from Spotify [@spotify], while weeks spent on the *Billboard Hot 100* were collected from Billboard [@billboard]. There were no similar datasets available that could have been used.

>>>>

The dataset used in this paper was created using data gathered from Spotify [@spotify] and Billboard [@billboard]. The data was collected by the authors for the purpose of this paper to investigate the number of Spotify streams based on weeks spent on the *Billboard Hot 100* for Beyoncé songs. Song titles, album titles, and the number of Spotify streams were collected from Spotify [@spotify], while weeks spent on the *Billboard Hot 100* were collected from Billboard [@billboard]. There were no similar datasets available that could have been used.
